Exploratory data analysis

### 2021-02-09 analysis/eda.Rmd
wflow_publish(knitr_in("analysis/eda.Rmd"), view = FALSE, verbose = TRUE)

pca_vi <- DataExplorer::plot_prcomp(vi_data_corrected_buffer2_no_defol_no_response,
  variance_cap = 0.90,
  ggtheme = ggpubr::theme_pubclean(),
  geom_label_args = list(size = 3),
  parallel = TRUE
)
pca_vi = pca_vi[[1]] +
  labs(title = "Target POV: 90%")
pca_vi
```

@@

```{r eda-18 }
plots <- list("Laukiz 1", "Laukiz 2", "Luiando", "Oiartzun")
dist <- map(plots, ~ {
  coords <- coords_vi_nri_clean_corrected %>%
    mutate(plot = factor(rep(
      c("Laukiz 1", "Laukiz 2", "Luiando", "Oiartzun"),
      c(559, 451, 301, 497)
    ))) %>%
    filter(plot == .x) %>%
    dplyr::select(-plot)
  points <- SpatialPoints(
    coords = coords,
    proj4string = CRS("+proj=utm +zone=30 +ellps=WGS84 +datum=WGS84 +units=m +no_defs")
  )
  distance <- mean(as.dist(pointDistance(points,
    allpairs = TRUE,
    lonlat = FALSE
  )))
})
set_names(dist, plots)
dist_plots <- unlist(dist)
```

>>>>

pca_vi <- DataExplorer::plot_prcomp(vi_data_corrected_buffer2_no_defol_no_response,
  variance_cap = 0.90,
  ggtheme = ggpubr::theme_pubclean(),
  geom_label_args = list(size = 3, nudge_y = 0.05),
  parallel = TRUE
)
pca_vi = pca_vi[[1]] +
  labs(title = "Target POV: 90%")
pca_vi[[1]]
```

@@

```{r eda-18 }
plots <- list("Laukiz 1", "Laukiz 2", "Luiando", "Oiartzun")
dist <- map(plots, ~ {
  coords <- coords_vi_nri_clean_corrected %>%
    mutate(plot = factor(rep(
      c("Laukiz 1", "Laukiz 2", "Luiando", "Oiartzun"),
      c(559, 451, 301, 497)
    ))) %>%
    filter(plot == .x) %>%
    dplyr::select(-plot)
  points <- SpatialPoints(
    coords = coords,
    # EPSG: 25830
    proj4string = CRS("+proj=utm +zone=30 +ellps=WGS84 +datum=WGS84 +units=m +no_defs")
  )
  distance <- mean(as.dist(pointDistance(points,
    allpairs = TRUE,
    lonlat = FALSE
  )))
})
set_names(dist, plots)
dist_plots <- unlist(dist)
```
